Multi-Task Mutual Learning for Vehicle Re-Identification

### 2019-05-13 paper.tex
Add final changes before submission.

\author{Georgia Rajamanoharan\\
Vision Semantics Ltd\\
{\tt\small georgia@visionsemantics.com}
% For a paper whose authors are all at the same institution,
% omit the following lines up until the closing ``}''.
% Additional authors and addresses can be added with ``\and'',
% just like the second author.
% To save space, use either the email address or home page, not both
\and
Aytac Kanaci \hspace{0.7cm}
%Queen Mary University of London\\
%{\tt\small secondauthor@i2.org}
%\and
Minxian Li  \hspace{0.7cm}
%Queen Mary University of London\\
%{\tt\small secondauthor@i2.org}
%\and
Shaogang Gong\\
Queen Mary University of London\\
{\tt\small \{a.kanaci,m.li,s.gong\}@qmul.ac.uk }
}

@@

\begin{figure*}[t]
  \begin{subfigure}{.6\textwidth}
    \includegraphics[width=\linewidth,trim=5cm 11cm 5cm 11cm,clip=true]{images/veri_orients.pdf}
  \end{subfigure}
  \begin{subfigure}{.4\textwidth}
    \centering
    \begin{tabular}{c | c | c}
      \hline
      Index & Orientation & Colour \\
      \hline
      0 & front & \textcolor{red}{red} \\
      1 & rear & - \\
      2 & left  & - \\
      3 & left front & \textcolor{cyan}{cyan}  \\
      4 & left rear & \textcolor{yellow}{yellow}  \\
      5 & right  & - \\
      6 & right front & \textcolor{green}{green} \\
      7 & right rear & \textcolor{black}{black} \\
      \hline
    \end{tabular}
  \end{subfigure}
  \caption{Examples from the VeRi776 dataset with the orientation labels provided in \cite{wang2017orientation} (best viewed in colour).}
  \label{F:veri_veh_orientations}
\end{figure*}

@@

During deployment, we employ the feature fusion layer from our trained model as the full feature representation in order to perform vehicle re-identification matching. As we do not necessarily have camera information about the query or gallery images, or timestamp information, which would allow the use of camera distance or time-based analysis, we use only a generic distance metric - the $L1$ metric - in order to match gallery images to the query. Hence, for each of the query image $\mathbf{I}^q$, and the gallery images $\{\mathbf{I}_i^g\}$,  we compute our $6400$ dimension fused feature representations, $\mathbf{x}^q$ and $\{\mathbf{x}_i^g\}$ respectively. We then calculate the $L1$ distance between the query representation and each of the gallery images, and rank the latter by increasing distance in order to calculate the Rank-1 and mAP performance scores.

@@

\begin{table}[h]
  \centering
  \begin{tabular}{l || c | c | c }
    \hline
    Method & mAP & Rank-1 & Rank-5 \\
    \hline
    MSVF \cite{kanaci2018vehicle} & 49.3 & 88.6 & - \\
    OIFE \cite{wang2017orientation} & 51.4 & 68.3 & 89.7 \\
    S-CNN+P-LSTM \cite{Shen_2017_ICCV} & 58.3 & 83.5 & 90.0 \\
    MTCRO \cite{xu2018framework} & 61.6 & 87.2 & 94.2 \\
    MTCRO (ReRank) \cite{xu2018framework} & 62.6 & 88.0 & 94.6 \\
    \hline
    MTML-S & 59.4 & 89.5 & 94.9 \\
    MTML-O & 60.8 & 90.2 & 95.4 \\
    MTML-G & 62.8 & 91.1 & 95.8 \\
    \hline
    MTML-SG & 63.7 & 90.6 & 95.8 \\
    MTML-OG & 63.5 & 92.0 & \bf{96.4}\\
    MTML-OSG & \bf{64.6} & \bf{92.3} & 95.7 \\
    MTML-OSG (ReRank) & \bf{\emph{68.3}} & 92.0 & 94.2 \\
    \hline
  \end{tabular}
  \caption{Trained/tested on VeRi776 only}
  \label{T:benchmark_results_veri}
\end{table}

@@

\subsection{Datasets}
We employ two Vehicle Re-ID datasets in our experiments, in order to train and test our method extensively. Firstly we conduct experiments on a benchmark dataset, VeRi776 \cite{liu2016veri}, which has been widely tested by the majority of recent works. And secondly we employ the new CityFlow dataset \cite{tang2019cityflow}, a challenging dataset that has been shown to be more difficult than previous publicly available benchmarks.
%
The VeRi-776 dataset \cite{liu2016veri} has 37,778 images of 576 IDs in the training set and 200
IDs in the test set. The standard probe and gallery sets consist of 1,678 and 11,579
images, respectively. There are also orientation labels, for 8 possible orientations, available for the VeRi-776 dataset, which were provided by \cite{Wang_2017_ICCV}.
%
%% The VehicleID \cite{liu2016vehicleid} dataset provides a training set with 113,346 from 13,164 IDs and a test set
%% with 19,777 images from 2,400 identities. It adopts the single-shot re-id setting,
%% with only one true matching for each probe. Following the standard setting, we
%% repeated 10 times of randomly selected probe and gallery sets in our experiments.
%
The CityFlow dataset \cite{tang2019cityflow} has 36,935 images of 333 IDs in the training set and 333 different IDs in the test set. The standard probe and gallery sets consist of 1,052 and 18,290 images respectively.
The data split statistics of both datasets are summarised in Table \ref{T:dataset_details}.

@@

\subsection{Evaluation on Veri776 Dataset}
Firstly, we train and test on the VeRi776 dataset in order to compare with
existing state-of-the-art methods with identical settings. In order to experiment the benefit of adding each of the separate branches of our model, we take branch A (vehicle identity) as our central branch, and of course all models have an E consensus branch, and then perform experiments where we include each of the other branches in turn. So MTML-S refers to a model built from branches A, B and E only, MTML-G has branches A, C and E only, and so on. We then test versions of the model with three branches (e.g. MTML-SG includes branches A, B, C and E).  
MTML-OSG (branches A, B, C, D and E) is then our full model, and MTML-OSG (ReRank \cite{zhong2017re}) the results of the full model after additional re-ranking. Table \ref{T:benchmark_results_veri} shows the results of this
experiment, with all experiments run for 150 epochs of training. As can be seen,
even before re-ranking, our full model achieves state-of-the-art mAP
and Rank-1 scores on this dataset, of 64.6\% and 92.3\%
respectively. And after re-ranking the mAP score is increased to an
impressive 68.3\%.

@@

%% \subsection{Evaluation on the VehicleID Dataset}
%% Second, we then train on both the VeRi776 and VehicleID datasets, and
%% test on VehicleID with all three of its test sets: small, medium and
%% large. We conducted this experiment to explore the benefit of training
%% model using additional orientation labels, as VeRi776 is the only
%% dataset available with orientation labels.

@@

%\begin{table}
%  \centering
%  \setlength{\tabcolsep}{0.01cm}
%  \begin{tabular}{l || c | c || c | c || c | c }
%    \hline
%    \multirow{2}{*}{Method} & \multicolumn{2}{c}{Small} & \multicolumn{2}{c}{Medium} &\multicolumn{2}{c}{Large} \\
%    \cline{2-7}
%    & mAP & Rank-1 & mAP & Rank-1 & mAP & Rank-1 \\
%    \hline
%    MTML-S & \\
%    MTML-O & \\
%    MTML-G & \\
%    % \hdashline
%    MTML-SG & \\
%    MTML-OG & \\
%    MTML-OSG & \\
%    % \hdashline
%    MTML-OSG+ReRank & \\
%    \hline
%  \end{tabular}
%  \caption{Trained on VeRi776+VehicleID, tested on VehicleID}
%  \label{T:benchmark_results_vehicleid}
%\end{table}

@@

\begin{table}[h]
  \centering
  \begin{tabular}{l || c | c | c }
    \hline
    Method & mAP & Rank-1 & Rank-5 \\
    \hline
    Resnet50 \cite{tang2019cityflow} & 25.5 & 41.3 & - \\
    \hline
    MTML-S  & 17.0 & 40.4 & 53.3 \\
    MTML-G  & 19.6 & 44.5 & 58.4 \\
    \hdashline
    MTML-SG & 20.6 & 44.1 & 55.8 \\
    \hdashline
    MTML-SG (ReRank) &  & & \\
    \hline
  \end{tabular}
  \caption{Trained/tested on CityFlow}
  \label{T:cityflow_results}
\end{table}

\begin{table}[h]
  \centering
  \setlength{\tabcolsep}{0.05cm}
  \begin{tabular}{l|c|c|c|c|c|c}
  \hline
  \multicolumn{1}{r|}{Test:} & \multicolumn{3}{c|}{VeRi-776} & \multicolumn{3}{c}{CityFlow} \\
  \hline
  Method       & mAP   & Rank-1  & Rank-5  & mAP   & Rank-1 & Rank-5  \\
  \hline
  MTML-O       &       &         &         &       &        &         \\
  MTML-S       &       &         &         &       &        &         \\
  MTML-G       & 61.6  & 89.7    & 95.1    & 22.3  & 47.4   & 57.3   \\
  MTML-SG      & 62.6  & 90.8    & 95.8    & 23.0  & 46.6   & 60.5   \\
  MTML-OG      &       &         &         &       &        &         \\
  MTML-OSG     &       &         &         &       &        &      \\
  \hline
  \end{tabular}
  \caption{Trained/tested on CityFlow+VeRi-776}
  \label{T:cf_veri_res}
\end{table}

@@

Two groups of experiments are conducted on CityFlow benchmark: 
(1) Training on CityFlow, and (2) Training on CityFlow and Veri-776.
%
For the first group experiment, we trained MTML-S (branch A, B and E), 
MTML-G (branch A, C and E) and MTML-SG model only on CityFlow training data.
Table \ref{T:cityflow_results} shows that: 
(1) -G branch combination is much better than -S branch combination. 
The potential reason is that grayscale analysis is more useful than mult-scale in vehicle Re-ID.
(2) Joint learning with -S and -G is better than any individual one of them on mAP evaluation.

%The reason of combine Veri-776 dataset into training set is that
Since the orientation label is only available in Veri-776, 
for training the full MTML model including orientation supervisory signal,
we did the second group experiment.
%
%Table \ref{T:cf_veri_res} shows that:

>>>>

\author{Georgia Rajamanoharan\\
Vision Semantics Ltd\\
{\tt\small georgia@visionsemantics.com}
% For a paper whose authors are all at the same institution,
% omit the following lines up until the closing ``}''.
% Additional authors and addresses can be added with ``\and'',
% just like the second author.
% To save space, use either the email address or home page, not both
\and
Ayta\c{c} Kanac\i \hspace{0.7cm}
%Queen Mary University of London\\
%{\tt\small secondauthor@i2.org}
%\and
Minxian Li  \hspace{0.7cm}
%Queen Mary University of London\\
%{\tt\small secondauthor@i2.org}
%\and
Shaogang Gong\\
Queen Mary University of London\\
{\tt\small \{a.kanaci,m.li,s.gong\}@qmul.ac.uk }
}

@@

\begin{figure*}[t]
  \begin{subfigure}{.6\textwidth}
    \includegraphics[width=\linewidth,trim=5cm 11cm 5cm 11cm,clip=true]{images/veri_orients.pdf}
  \end{subfigure}
  \begin{subfigure}{.4\textwidth}
    \centering
    \begin{tabular}{c | c | c}
      \hline
      Index & Orientation & Colour \\
      \hline
      0 & front & \textcolor{red}{red} \\
      1 & rear & - \\
      2 & left  & - \\
      3 & left front & \textcolor{cyan}{cyan}  \\
      4 & left rear & \textcolor{yellow}{yellow}  \\
      5 & right  & - \\
      6 & right front & \textcolor{green}{green} \\
      7 & right rear & \textcolor{black}{black} \\
      \hline
    \end{tabular}
  \end{subfigure}
  \caption{Examples from the VeRi-776 dataset with the orientation labels provided in \cite{wang2017orientation} (best viewed in colour).}
  \label{F:veri_veh_orientations}
\end{figure*}

@@

During deployment, we employ the feature fusion layer from our trained model as the full feature representation in order to perform vehicle re-identification matching. As we do not necessarily have camera information about the query or gallery images, or timestamp information, which would allow the use of camera distance or time-based analysis, we use only a generic distance metric - the $L2$ metric - in order to match gallery images to the query. Hence, for each of the query image $\mathbf{I}^q$, and the gallery images $\{\mathbf{I}_i^g\}$,  we compute our $6400$ dimension fused feature representations, $\mathbf{x}^q$ and $\{\mathbf{x}_i^g\}$ respectively. We then calculate the $L2$ distance between the query representation and each of the gallery images, and rank the latter by increasing distance in order to calculate the Rank-1 and mAP performance scores.

@@

\begin{table}[h]
  \centering
  \begin{tabular}{l || c | c | c }
    \hline
    Method & mAP & Rank-1 & Rank-5 \\
    \hline
    MSVF \cite{kanaci2018vehicle} & 49.3 & 88.6 & - \\
    OIFE \cite{wang2017orientation} & 51.4 & 68.3 & 89.7 \\
    S-CNN+P-LSTM \cite{Shen_2017_ICCV} & 58.3 & 83.5 & 90.0 \\
    MTCRO \cite{xu2018framework} & 61.6 & 87.2 & 94.2 \\
    MTCRO (ReRank) \cite{xu2018framework} & 62.6 & 88.0 & 94.6 \\
    \hline
    MTML-S & 59.4 & 89.5 & 94.9 \\
    MTML-O & 60.8 & 90.2 & 95.4 \\
    MTML-G & 62.8 & 91.1 & 95.8 \\
    \hline
    MTML-SG & 63.7 & 90.6 & 95.8 \\
    MTML-OG & 63.5 & 92.0 & \bf{96.4}\\
    MTML-OSG & \bf{64.6} & \bf{92.3} & 95.7 \\
    MTML-OSG (ReRank) & \bf{\emph{68.3}} & 92.0 & 94.2 \\
    \hline
  \end{tabular}
  \caption{Trained/tested on VeRi-776 only}
  \label{T:benchmark_results_veri}
\end{table}

@@

\subsection{Datasets}
We employ two Vehicle Re-ID datasets in our experiments, in order to train and test our method extensively. Firstly we conduct experiments on a benchmark dataset, VeRi-776 \cite{liu2016veri}, which has been widely tested by the majority of recent works. And secondly we employ the new CityFlow dataset \cite{tang2019cityflow}, a challenging dataset that has been shown to be more difficult than previous publicly available benchmarks.
%
The VeRi-776 dataset \cite{liu2016veri} has 37,778 images of 576 IDs in the training set and 200
IDs in the test set. The standard probe and gallery sets consist of 1,678 and 11,579
images, respectively. There are also orientation labels, for 8 possible orientations, available for the VeRi-776 dataset, which were provided by \cite{Wang_2017_ICCV}.
%
%% The VehicleID \cite{liu2016vehicleid} dataset provides a training set with 113,346 from 13,164 IDs and a test set
%% with 19,777 images from 2,400 identities. It adopts the single-shot re-id setting,
%% with only one true matching for each probe. Following the standard setting, we
%% repeated 10 times of randomly selected probe and gallery sets in our experiments.
%
The CityFlow dataset \cite{tang2019cityflow} has 36,935 images of 333 IDs in the training set and 333 different IDs in the test set. The standard probe and gallery sets consist of 1,052 and 18,290 images respectively.
The data split statistics of both datasets are summarised in Table \ref{T:dataset_details}.

@@

\subsection{Evaluation on Veri776 Dataset}
Firstly, we train and test on the VeRi-776 dataset in order to compare with
existing state-of-the-art methods with identical settings. In order to experiment the benefit of adding each of the separate branches of our model, we take branch A (vehicle identity) as our central branch, and of course all models have an E consensus branch, and then perform experiments where we include each of the other branches in turn. So MTML-S refers to a model built from branches A, B and E only, MTML-G has branches A, C and E only, and so on. We then test versions of the model with three branches (e.g. MTML-SG includes branches A, B, C and E).  
MTML-OSG (branches A, B, C, D and E) is then our full model, and MTML-OSG (ReRank \cite{zhong2017re}) the results of the full model after additional re-ranking. Table \ref{T:benchmark_results_veri} shows the results of this
experiment, with all experiments run for 150 epochs of training. As can be seen,
even before re-ranking, our full model achieves state-of-the-art mAP
and Rank-1 scores on this dataset, of 64.6\% and 92.3\%
respectively. And after re-ranking the mAP score is increased to an
impressive 68.3\%.

@@

%% \subsection{Evaluation on the VehicleID Dataset}
%% Second, we then train on both the VeRi-776 and VehicleID datasets, and
%% test on VehicleID with all three of its test sets: small, medium and
%% large. We conducted this experiment to explore the benefit of training
%% model using additional orientation labels, as VeRi-776 is the only
%% dataset available with orientation labels.

@@

%\begin{table}
%  \centering
%  \setlength{\tabcolsep}{0.01cm}
%  \begin{tabular}{l || c | c || c | c || c | c }
%    \hline
%    \multirow{2}{*}{Method} & \multicolumn{2}{c}{Small} & \multicolumn{2}{c}{Medium} &\multicolumn{2}{c}{Large} \\
%    \cline{2-7}
%    & mAP & Rank-1 & mAP & Rank-1 & mAP & Rank-1 \\
%    \hline
%    MTML-S & \\
%    MTML-O & \\
%    MTML-G & \\
%    % \hdashline
%    MTML-SG & \\
%    MTML-OG & \\
%    MTML-OSG & \\
%    % \hdashline
%    MTML-OSG+ReRank & \\
%    \hline
%  \end{tabular}
%  \caption{Trained on VeRi-776+VehicleID, tested on VehicleID}
%  \label{T:benchmark_results_vehicleid}
%\end{table}

@@

%%% Old %50 percent table %%%
% \begin{table}[h]
%   \centering
%   \begin{tabular}{l || c | c | c }
%     \hline
%     Method & mAP & Rank-1 & Rank-5 \\
%     \hline
%     Resnet50 \cite{tang2019cityflow} & 25.5 & 41.3 & - \\
%     \hline
%     MTML-S  & 17.0 & 40.4 & 53.3 \\
%     MTML-G  & 19.6 & \bf 44.5 & \bf 58.4 \\
% %    \hdashline
%     \hline
%     MTML-SG & \bf{20.6} & 44.1 & 55.8 \\
% %    \hdashline
%     MTML-SG (ReRank) & \bf{\emph {25.7}} & 43.4 & 47.2 \\
%     \hline
%   \end{tabular}
%   \caption{Trained/tested on CityFlow}
%   \label{T:cityflow_results}
% \end{table}

\begin{table}[h]
  \centering
  \begin{tabular}{l || c | c | c }
    \hline
    Method & mAP & Rank-1 & Rank-5 \\
    \hline
    Resnet50 \cite{tang2019cityflow} & 25.5 & 41.3 & - \\
    \hline
    MTML-S  & 17.0 & 40.4 & 53.3 \\
    MTML-G  & 19.6 & 44.5 & 58.4 \\
    \hdashline
    MTML-SG & 20.6 & 44.1 & 55.8 \\
    \hdashline
    MTML-SG (ReRank) & 25.7 & 43.4 & 47.2 \\
    \hline
  \end{tabular}
  \caption{Trained/tested on CityFlow}
  \label{T:cityflow_results}
\end{table}

\begin{table}[h]
  \centering
  \setlength{\tabcolsep}{0.05cm}
    \begin{tabular}{p{2cm}|c|c|c|c|c|c}
  \hline
  \multicolumn{1}{r|}{} & \multicolumn{3}{c|}{VeRi-776} & \multicolumn{3}{c}{CityFlow} \\
  \hline
  Method       & mAP   & Rank-1  & Rank-5  & mAP   & Rank-1 & Rank-5  \\
  \hline
% %50 percent results
%   MTML-S       & 58.4  & 88.5    & 94.6    & 19.7  & 42.4   & 56.0    \\
%   MTML-O       & 59.2  & 89.9    & 94.9    & 20.9  & 46.6   & 59.6    \\
%   MTML-G       & 61.6  & 89.7    & 95.1    & 22.3  & 47.4   & 57.3   \\
%   \hline
%   MTML-SG      & 62.6  & 90.8    & \bf{95.8}    & 23.0  & 46.6   & 60.5   \\
%   MLML-OG      & 62.0  & 91.2    & 95.6    & 23.8  & 49.1   & 60.9    \\
%   MTML-OSG    & \bf{62.6}  & 90.6    & 95.5   & \bf{24.6}  & \bf{51.1}   & \bf{61.5} \\
%   MTML-OSG (ReRank)   & \bf{\emph{66.4}}  & \bf{91.5}    & 93.6   & \bf{\emph{30.4}}  & 50.9   & 53.7 \\
  MTML-S       & 58.4  & 88.5    & 94.6    & 18.9  & 40.6   & 53.3   \\
  MTML-O       & 59.2  & 89.9    & 94.9    & 20.3  & 44.3   & 56.0   \\
  MTML-G       & 61.6  & 89.7    & 95.1    & 21.6  & 46.1   & 57.5   \\
    \hdashline
  MTML-SG      & 62.6  & 90.8    & \bf{95.8}  & 22.1  & 45.8  & 56.5   \\
  MLML-OG      & 62.0  & \bf{91.2}  & 95.6    & 22.9  & 46.6  & 58.2    \\
  MTML-OSG     & \bf{62.6}  & 90.6   & 95.5   & \bf{23.6}  & \bf{48.9}  & \bf{59.7}   \\
    \hdashline
  MTML-OSG (ReRank)   & \bf{\emph{66.4}}  & 91.5  & 93.6  & \bf{\emph{29.2}}  & 48.8 & 50.7  \\
  \hline
  \end{tabular}
  \caption{Trained/tested on CityFlow+VeRi-776}
  \label{T:cf_veri_res}
\end{table}

\begin{figure*}[ht]
    \centering
    \renewcommand{\arraystretch}{2.8}
    \begin{tabular}{rcl}
        & \textbf{AP} & \textbf{Query - Ranks(1-10)} \\ 
    \multirow{2}{*}{\textbf{a)}} & 0.34        &  \multirow{2}{*}{\begin{minipage}{0.7\textwidth} \includegraphics[width=\linewidth]{images/pair_a.png} \end{minipage} }  \\
                                 & 0.51        &                        \\

    \multirow{2}{*}{\textbf{b)}} & 0.19        &  \multirow{2}{*}{\begin{minipage}{0.7\textwidth} \includegraphics[width=\linewidth]{images/pair_b.png} \end{minipage} }  \\
                                 & 0.81        &                        \\

    \multirow{2}{*}{\textbf{c)}} & 0.09        &  \multirow{2}{*}{\begin{minipage}{0.7\textwidth} \includegraphics[width=\linewidth]{images/pair_c.png} \end{minipage} }  \\
                                 & 0.18        &                        \\

    \multirow{2}{*}{\textbf{d)}} & 0.33        &  \multirow{2}{*}{\begin{minipage}{0.7\textwidth} \includegraphics[width=\linewidth]{images/pair_d.png} \end{minipage} }  \\
                                 & 1.0         &                       
    \end{tabular}
    \renewcommand{\arraystretch}{1}
%	\vspace{-0.2cm}

    \caption{
        Qulitative comparison of example query images between expriment with
        and without orientaion branch.
        Rank-1 to Rank-10 is shown. Each pair compares MTML-SG
        (upper) to MTML-OSG (below) trained and tested on the VeRi-776. 
        AP refers to Average Precision of that query. 
    }
    \label{fig:ranks}
%    \vspace{-0.7cm}
\end{figure*}

@@

Two groups of experiments are conducted on CityFlow benchmark: 
(1) Training on CityFlow, and (2) Training on CityFlow and VeRi-776.
%
For the first group experiment, we trained MTML-S (branch A, B and E), 
MTML-G (branch A, C and E) and MTML-SG model only on CityFlow training data.
Table \ref{T:cityflow_results} shows that: 
(1) -G branch combination is much better than -S branch combination. 
The potential reason is that grayscale analysis is more useful than mult-scale in vehicle Re-ID.
(2) Joint learning with -S and -G is better than any individual one of them on mAP evaluation.
Another interesting thing is that
after re-ranking algorithm, mAP performance improves while CMC performace drops.
The possible reason is that more similar image vehicles will get close after re-ranking.
This means some false matching images at high rank will ``attract'' more false matching images after re-ranking.
In such a case, it will impact CMC performance.

%The reason of combine VeRi-776 dataset into training set is that
Since the orientation label is only available in VeRi-776, 
for training the full MTML model including orientation supervisory signal,
we did the second group experiment.
%
Table \ref{T:cf_veri_res} shows that: 
(1) By adding VeRi-776 training data,
with MTML-S, MTML-G and MTML-SG, 
we all obtain the better mAP and CMC performance on CityFlow
than the model only training on CityFlow.
Meanwhile, the mAP and CMC performance is a slightly lower on VeRi-776
than the model only training on VeRi-776. We suspect this is due to training
for 100 epochs, compared to 150.
(2) By adding orientation branch, MLTML-OSG totaling 4 bracnhes, 
we obtian the best mAP performance {62.6\%} and {23.6\%} on VeRi-776 and
CityFlow repectively. 
This shows that our mutual learning between orientation branch supervised by orientation label and other branches supervised by ID label is effective.

%(1) After including Veri776 data for training orientation branch (O branch),
%we get a better mAP performance (23.8\%) than only tr on CityFlow dataset.
%(2) we can get the best mAP performance XXX\% and XXX\% 
%on VeRi-776 and CityFlow respectively
%by combining all branches of our model.

Qualitative result comparison with or without orientation branch are shown in
Figure~\ref{fig:ranks}. The advantage of learning orientation and ID signal can
be seen in each pair where in MTML-OSG different views of the same ID vehicle
are ranked higher compared to MTML-SG (Figure~\ref{fig:ranks}(a,b,d)). It can also be observerd that similar
viewpoints better grouped together in the ranks (Figure~\ref{fig:ranks}(c,d)).
